Project Report\\\textsc{DEVS Ex Machina}

### 2015-04-25 manual/tex/reqs.tex
Addition of short Documentation section to manual

>>>>

\subsubsection{Documentation}
Generating the source documentation is optional and requires Doxygen to be installed. UML and other diagrams will only be created if Graphviz is installed.\\
After building the source, enter the \textsl{build} folder and enter the command 
\begin{verbatim}
$ make doc
\end{verbatim} This will generate all documentation in the \textsl{doc} folder.
